% ======================================================================
% Title: Lecture Notes for MATH1032-01
% Author: Joshua W. Kelly
% Class: MATH1032-01
% Prof. Camren Morgan 
% Date: August 30, 2024
% ======================================================================
\documentclass{notes}
\begin{document}

\maketitle % Creates the title page

\section*{Author's Note} % Section without numbering
These lecture notes are a compilation of material from the course Analytic Geometry and Calculus I (MATH1032) at La Roche University for the Fall 2024 Semester, supplemented with personal notes and reflections on the subject matter. My notes may be accessed at \\ \url{https://github.com/JoshuaWKelly/MATH1032-01-Lecture_Notes/tree/main}. The formatting and style of these notes are inspired by the Feynman Lectures on Physics (\url{https://www.feynmanlectures.caltech.edu/}), and aim to present the concepts of calculus and analytic geometry in an engaging and accessible manner -- similar to how Richard Feynman conveyed complex physics topics.

The content primarily draws from \textit{Calculus Volume 1} by Gilbert Strang et al.\cite{strang_calculus_2016}, a foundational text that provides a thorough introduction to calculus. Problems, examples, and exercises referenced in these notes are sourced directly from this textbook unless otherwise noted. The intention is to provide students with a resource that not only follows the course curriculum but also adds depth and clarity to the material covered in lectures.

I hope these notes serve as a helpful guide for anyone studying calculus and encourage further exploration and understanding of the subject.\\

\noindent{Joshua W. Kelly} \\
\textit{La Roche University} \\ 

\newpage

\vfill

\section*{CC0 1.0 Universal (CC0 1.0) Public Domain Dedication}

\textbf{No Copyright}  
\faCreativeCommons~This work is dedicated to the public domain under the Creative Commons Zero (CC0) license. To the extent possible under law, the author has waived all copyright and related or neighboring rights to this work. 

You can copy, modify, distribute and perform the work, even for commercial purposes, all without asking permission. For more information, see \url{https://creativecommons.org/publicdomain/zero/1.0/}.

\tableofcontents % Creates a table of contents

\newpage

\input{chapter-1.tex}

\input{chapter-2.tex}

\input{chapter-3.tex}

\input{chapter-4.tex}

% Biblography 

\printbibliography

\newpage

\input{appendix.tex}

\end{document}